tl20-05_berghei_pir_GeneSetEnrichmentQusage

### 2021-10-01 chapter3_results_bergheiPir/Manuscript_berghei_pir_GeneSetEnrichmentQusage.Rmd
Fix heatmap labels Qusage which were wrong

```{r load_packages}
library('dplyr')
library('readr')
library('readxl')
library('data.table')
library('tibble')
library('qusage')
library('ggplot2')
library('stringr')
library('RColorBrewer')
library('writexl')
```

@@

png(filename = "plots/thesis_chapter3_figure_statsCompHeatmap_geneGroups.png",
    width = 7,
    height = 5,
    units = "in",
    res = 330)
Heatmap(all_stats_df_cast,
        name = 'logFoldChange',
        cluster_rows = FALSE,
        cluster_columns = FALSE,
        rect_gp = gpar(col = "white", lwd = 2),
        cell_fun = function(j, i, x, y, width, height, fill){
          stat_df <- all_stats_df[all_stats_df$contrast == rownames(all_stats_df_cast[i,]),]
          fdr_val <- stat_df$FDR[j]
          logfold <- stat_df$log.fold.change[j]
          if(fdr_val<= 0.05){
            grid.text(
              sprintf("%.3f", #One significant figure
                      fdr_val),
              x,
              y,
              gp = gpar(fontsize = 10,
                        fontface = 'bold',
                        col = ifelse(logfold > 2, 'white', 'black'))
            )
          }
        })
dev.off()
```

>>>>

```{r load_packages}
library('dplyr')
library('readr')
library('readxl')
library('data.table')
library('tibble')
library('qusage')
library('ggplot2')
library('stringr')
library('RColorBrewer')
library('writexl')
library('ComplexHeatmap')
```

@@

png(filename = "plots/thesis_chapter3_figure_statsCompHeatmap_geneGroups.png",
    width = 7,
    height = 5,
    units = "in",
    res = 330)
Heatmap(all_stats_df_cast,
        name = 'logFoldChange',
        cluster_rows = FALSE,
        cluster_columns = FALSE,
        rect_gp = gpar(col = "white", lwd = 2),
        cell_fun = function(j, i, x, y, width, height, fill){
          stat_df <- all_stats_df[all_stats_df$contrast == rownames(all_stats_df_cast)[i],]
          stat_df <- stat_df[stat_df$pathway.name == colnames(all_stats_df_cast)[j],]
          fdr_val <- stat_df$FDR
          logfold <- stat_df$log.fold.change
          if(fdr_val <= 0.05){
            grid.text(
              sprintf("%.3f", #One significant figure
                      fdr_val),
              x,
              y,
              gp = gpar(fontsize = 10,
                        fontface = 'bold',
                        col = ifelse(logfold > 2, 'white', 'black'))
            )
          }
        })
dev.off()
```
